Modalities for Location Virtualization

### 2022-09-19 programlogic.tex
+

\section{Program Logic for Location Virtualization}
\label{sec:logic}
In this section, we describe our high-level reasoning principles for location virtualization whose detailed justification is shown in \sref{sec:soundness}. 
\subsection{Points-To Assertions}
\label{sec:pointsto}

@@

\end{array}
\]
\caption{Virtual Points-to Relation}
  \label{fig:virtualpointsto}
\end{figure*}
\todo{iso todo: stress fractions and aligment}
\subsection{Modal Abstraction for Virtualizing Memory Locations}
\label{sec:modallocationvirtualization}
\input{fig-laws}
The most essential part of our reasoning principles is shaped around abstractions for location virtualization, more concretely virtual memory points-to relation in Figure \fref{fig:virtualpointsto}. One might have already noticed that the resource represented by the virtual-points to is not only a simple immediately mapped singly resource but also
\begin{itemize}
\item a tree-like structured resrouce rooted at the certain physical memory address ($\crt$) -- not a single resource mapping abstraction 
\item the shared indirection levels abstracted as mappings with fractional permissions
\item through partially owned set of resource mappings grants the eventual uniquely ownable single resource, i.e. page address 
\end{itemize}

>>>>

\section{Program Logic for Location Virtualization}
\label{sec:logic}
In this section, we describe our high-level reasoning principles for location virtualization whose detailed justification is shown in \sref{sec:soundness}. Here we present our reasoning principle shaped around understanding the virtual address space, specifially the opeations using virtual points-to mappings.
\subsection{Points-To Assertions}
\label{sec:pointsto}

@@

\end{array}
\]
\caption{Virtual Points-to Relation}
  \label{fig:virtualpointsto}
\end{figure*}
\todo{iso todo: stress fractions and aligment}
\subsection{Modal Abstraction for Virtualizing Memory Locations}
\label{sec:modallocationvirtualization}
\input{fig-laws}
The most essential part of our reasoning principles is shaped around abstractions for location virtualization, more concretely virtual memory points-to relation in Figure \fref{fig:virtualpointsto}. One might have already noticed that the resource represented by the virtual-points to is not only a simple immediately mapped singly resource but also
\begin{itemize}
\item a tree-like structured resrouce rooted at the certain physical memory address ($\crt$) -- not a single resource mapping abstraction 
\item the shared indirection levels abstracted as mappings with fractional permissions
\item through partially owned set of resource mappings grants the eventual uniquely ownable single resource, i.e. page address 
\end{itemize}
which we think can be well-summarized with the modal abstraction shown in \RULE{ModalLocVirt} which allows us to have
\begin{itemize}
  \item \textbf{contingency}: the fact $\modalP$ holds \textit{at} on the resrouces \textit{hidden-under} the physical location $\ell$ (e.g. $\crt$)
  \item \textbf{hiding states}: hide the indirection abstracted as page-table mappings through the local-state modality
  \item \textbf{composing local-states}: allows c
\end{itemize}
